---
title: "Prints: rjd3x13 Holes"
format: html
---

## Load and raw data 
```{r}
## be on develop version 
library("rjd3toolkit")
library("rjd3x13")
y<-ABS$X0.2.14.10.M
str(y)
plot(y)
```

## Prints (voir T, july TP)

- model span in print summary 

JD3_X13_RSLTS vs JD3_X13_OUTPUT ?

## Bias spec pb 

- of mode Log additive can be bias set to NONE ? or at least ratio ?

- simulate series with potentially high bias , and test 

- in JD+ doc book + details provide details on bais formeula 




### Mode

back this up with java 
- improve explanation 
if pre-adjustemnt

without pred-adjustment 

cf GUi 

### obj first layer doc to avoid big mistakes: JULY 2026

- release end of july 

### obj 2: october release 

- clean formaulas and tests for mode and bias 



## philo

- if a parameter can be se in spec : should be visible in psec print 
ex bias, mode 

- if a parameter can be selected by algo: ex seaso and trend filters 
should de printed in results 


- series span and estimation span should be printed in results 


### Issues and Mails to set up 

keep it all in this file 



### Add bias and mode tp spec print 

mode will be called mode X-11 to draw attention specific part 

```{r}


### problem no TRACE of specified pparams 
## 
spec_init<-x13_spec()
spec_init
## has transfo to be set to log to be able to estimate : NO ! (the case in GUI ?)
spec_ud <- set_x11(spec_init,
     mode = "LogAdditive",
     seasonal.comp = 1,
     seasonal.filter = "S3X9",
     henderson.filter = 7,
     lsigma = 1.7,
     usigma = 2.7,
     fcasts = -1,
     bcasts = -1,
     calendar.sigma = "All",
     sigma.vector = NA,
     exclude.forecast = FALSE,
     bias= "NA"
 )
# bias=..



spec_ud

class(spec_ud)

sa_x13_ud <- rjd3x13::x13(y,spec_ud)

sa_x13_ud$result$preprocessing$description$log
summary(sa_x13_ud)

spec_ud$x11$


# if transfo set to add ?
spec_init<-x13_spec()

spec_init
spec_ud <- set_transform(spec_init,fun="NONE")
spec_ud
## has transfo to be set to log to be able to estimate : NO ! (the case in GUI ?)
spec_ud <- set_x11(spec_ud,
     mode = "LogAdditive",
     seasonal.comp = 1,
     seasonal.filter = "S3X9",
     henderson.filter = 7,
     lsigma = 1.7,
     usigma = 2.7,
     fcasts = -1,
     bcasts = -1,
     calendar.sigma = "All",
     sigma.vector = NA,
     exclude.forecast = FALSE,
     bias= "NA"
 )

spec_ud

# creating something incoherent: pe adj: level and log additive !
### estimation works : warning missing ? or doc ?

sa_test<-x13(y,spec_ud)
summary(sa_test)
##mode and biais cannot be retrieved to see what happened ?

## preadj mode is here 
### in results 
sa_test$result$preprocessing$description$log
### in result_spec 
sa_test$result_spec$regarima$transform$fn
## X11 mode ? HERE 
### in results 
sa_test$result$preadjust

### in result_spec : not operating 
sa_test$result_spec$x11$mode
## not applied I guess
                   
## if add model detected automatically what happens ?



```

## Test additive compbine with pseudo additive 


## Test mode X11 without preadj spec 

questions :
Can mode be set to "Undefined" here and estimation work 

```{r}
spec_x11_i<-x11_spec()
spec_x11_i 

# multiplicative by default
spec_ud <- set_x11(spec_x11_i,
     seasonal.comp = 1,
     seasonal.filter = "S3X9",
     henderson.filter = 7,
     lsigma = 1.7,
     usigma = 2.7,
     fcasts = -1,
     bcasts = -1,
     calendar.sigma = "All",
     sigma.vector = NA,
     exclude.forecast = FALSE,
     bias= "NA"
 )
spec_ud
sa_x11<-x11(AirPassengers,spec_ud)
sa_x11$d10

# if set to "Undefined", displayed as UNKOWN: what happens: additive ?

c(NA, "Undefined", "Additive", "Multiplicative", "LogAdditive", "PseudoAdditive")

# if set to pseudo additive : then a multiplicative d10 ??

spec_ud <- set_x11(spec_x11_i,
     mode = "PseudoAdditive",
     seasonal.comp = 1,
     seasonal.filter = "S3X9",
     henderson.filter = 7,
     lsigma = 1.7,
     usigma = 2.7,
     fcasts = -1,
     bcasts = -1,
     calendar.sigma = "All",
     sigma.vector = NA,
     exclude.forecast = FALSE,
     bias= "NA"
 )

spec_ud
sa_x11<-x11(AirPassengers,spec_ud)
sa_x11$d10




# estimation: happens : but how to know the chosen mode ?
## add user defined output ?
sa_x11<-x11(AirPassengers,spec_ud)

ud<-rjd3x13::x13_dictionary()
sa_x11<-x11(y,spec_ud,userdefined = ud)

sa_x11$user_defined$mode # undefined, so really used: has to be det with d10 ?
sa_x11$user_defined$d10
sa_x11$user_defined$y
plot(sa_x11$d10) # level 
lines(sa_x11)
# ## plot ne marche pas
# plot(sa_x11)

################ HUGE souci

## IMPROVE X11 results : no result spec = PB 
sa_x11$user_defined$

```


### Add bias and mode  to model summary 

```{r}

sa_x13_ud <- rjd3x13::x13(y,spec_ud)
sa_x13_ud
class(sa_x13_ud)
summary(sa_x13_ud)


```


### check estimation span

```{r}

```




#### Navigating spec 

```{r}
str(x13_spec_user_defined)
x13_spec_user_defined$regarima$regression$td$lp

```

## X11 function and x11 spec 

### pb diplay of results 

"rien", même dans user-defined 

### qd mode incoherent ou mal défini que se passe t il ?

pas de restriction sur mode 

