---
title: "T-rjd3x13 Mode Biais Sigma vector"
format: html
---

```{r}
#| label: loading-rjdverse
#| echo: true
#| eval: true
library("rjd3toolkit")
library("rjd3x13")
```

# Objectifs

- key reproducible format of testing (pre-vignette)
- pré vignette ? (as testing tool)

- check mode !! + formulas + self verif + hd+ online doc
- check composite seasonal filters
- check sigma vector and illustrate it

### Issue 1: biais doc


from jp R code demo 

```{r}

#' Title
#'
#' @param y (linearized) Numerics. original series, perhaps corrected for deterministic effects. In that case it's exp(linearized). 
#' @param lt Numerics. trend of log(y)
#' @param ls Numerics. seasonal or periodic component of log(y)
#' @param li Numerics. irregular component of log(y)
#' @param period Numerics. Length of a cycle (of the periodic component)
#'
#' @return A data.frame with y, t, s, i, so that y=t*s*i
#' @details Based on the bias correction in SEATS. 
#' @examples
biasCorrection<-function(y, lt, ls, li, period){
  # TO DO. Check possible numerical problems in the canonical decomposition (ly != lt+ls+li) and throw a warning if differences are inacceptable
  t<-exp(lt)
  s<-exp(ls)
  i<-exp(li)
  n<-length(y)
  # rounding for non integer periods
  nc<-round(length(y)-n%%period)
  sbias<-mean(s[1:nc]) # sur l'ensemble de la periode (années completes) et pas année par année 
  s<-s/sbias
  ibias<-mean(i)
  t<-t*(ibias*sbias)
  # we correct some numerical problems that way (as in SEATS)
  sa<-y/s
  i<-sa/t
  
  return(data.frame(y=y, sa=sa, t=t, s=s, i=i))
}

## Test on tramo-seats SA data : is bias corrected 

```


TEST x11

see doc christiane 

```{r}

library("rjd3tramoseats")

# chgt de bais

# decocher bais

y <- rjd3toolkit::ABS$X0.2.09.10.M
s1<-rjd3tramoseats::tramoseats_spec("rsafull")
s2<-set_transform(
  s1,"Log")
# recup les comps en log 
summary(tramoseats_dictionary())
View(tramoseats_full_dictionary())

# Extract names of output of interest
user_defined_output <- tramoseats_dictionary()[tramoseats_dictionary() %in% c("y","ylin","s","t","i","decomposition.y_lin", 
"decomposition.sa_lin",
 "decomposition.t_lin",
 "decomposition.s_lin",
 "decomposition.i_lin",
 "decomposition.y_cmp",
 "decomposition.sa_cmp",
 "decomposition.t_cmp",
 "decomposition.s_cmp",
 "decomposition.i_cmp")]

user_defined_output

# Generate the corresponding output in an estimation
y <- rjd3toolkit::ABS$X0.2.09.10.M
m <- tramoseats(y, "rsafull", s2, userdefined=user_defined_output)
tail(m$user_defined)
# finaux en niveau 
 y<- m$user_defined$y
 s<- m$user_defined$s
 t<- m$user_defined$t
 i<- m$user_defined$i
ylin<- m$user_defined$ylin # doublon ? y lin en niveau 
# decomp serie linearisée en log
decomposition.y_lin<- m$user_defined$decomposition.y_lin # en log
decomposition.sa_lin<- m$user_defined$decomposition.sa_lin
decomposition.s_lin<-m$user_defined$decomposition.s_lin
decomposition.t_lin<- m$user_defined$decomposition.t_lin
decomposition.i_lin<- m$user_defined$decomposition.i_lin
# remise decomposition en niveau 
decomposition.y_cmp<- m$user_defined$decomposition.y_cmp  #y lin en niveau ? doublon 
decomposition.sa_cmp<- m$user_defined$decomposition.sa_cmp
decomposition.t_cmp<- m$user_defined$decomposition.t_cmp
decomposition.s_cmp<- m$user_defined$decomposition.s_cmp
decomposition.i_cmp<- m$user_defined$decomposition.i_cmp  

# visualiser, comparer, identifier: valider appellation

# verif egalites log vs niveau 
## y lin 
li<-round(decomposition.y_lin-log(ylin),6)
li
all.equal(decomposition.y_lin,log(ylin))
li2<-round(ylin-decomposition.y_cmp,6)
li2
all.equal(ylin,decomposition.y_cmp)
# la decomposition est faite en log et remise en niveau 
# sa : là on devrait voir si correction biais 
sa_d <-round(exp(decomposition.sa_lin)-decomposition.sa_cmp,6)
sa_d

# biais

# t : là on devrait voir si correction biais (remise)
t_d <-round(exp(decomposition.t_lin)-decomposition.t_cmp,6)
t_d

# s : là on devrait voir si correction biais moyenne à 1 ?
s_d <-round(exp(decomposition.s_lin)-decomposition.s_cmp,6)
s_d
# rounding for non integer periods
nc<-round(length(y)-length(y)%%12)
 nc
mean(decomposition.s_lin[1:nc])
mean(exp(decomposition.s_lin)[1:nc])
mean(decomposition.s_cmp[1:nc])

### ajouter par periode (idem que mean global ou pas, non )

# i : là on devrait voir si correction biais moyenne à 1 ?
i_d <-round(exp(decomposition.i_lin)-decomposition.i_cmp,6)
i_d
mean(decomposition.i_lin)
mean(exp(decomposition.i_lin))
mean(decomposition.i_cmp) # a ete corrigé 

### on veut mean (ylin)= mean (sa_lin)
mean(ylin)
mean(decomposition.sa_cmp)
# petit ecart 


###################################################

# bias correction deactivated puis calcul JP 
s3<-set_seats(s2,bias=NA)
# Generate the corresponding output in an estimation
y <- rjd3toolkit::ABS$X0.2.09.10.M
m1 <- tramoseats(y, "rsafull", s3, userdefined=user_defined_output)

 
 # finaux en niveau 
 y1<- m1$user_defined$y
 s1<- m1$user_defined$s
 t1<- m1$user_defined$t
 i1<- m1$user_defined$i
ylin1<- m1$user_defined$ylin # doublon ? y lin en niveau 
# decomp serie linearisée en log
decomposition.y_lin1<- m1$user_defined$decomposition.y_lin # en log
decomposition.sa_lin1<- m1$user_defined$decomposition.sa_lin
decomposition.s_lin1<-m1$user_defined$decomposition.s_lin
decomposition.t_lin1<- m1$user_defined$decomposition.t_lin
decomposition.i_lin1<- m1$user_defined$decomposition.i_lin
# remise decomposition en niveau 
decomposition.y_cmp1<- m1$user_defined$decomposition.y_cmp  #y lin en niveau ? doublon 
decomposition.sa_cmp1<- m1$user_defined$decomposition.sa_cmp
decomposition.t_cmp1<- m1$user_defined$decomposition.t_cmp
decomposition.s_cmp1<- m1$user_defined$decomposition.s_cmp
decomposition.i_cmp1<- m1$user_defined$decomposition.i_cmp  

# visualiser, comparer, identifier: valider appellation

# verif egalites log vs niveau 
## y lin1 
li<-round(decomposition.y_lin1-log(ylin1),6)
li
all.equal(decomposition.y_lin1,log(ylin1))
li2<-round(ylin1-decomposition.y_cmp1,6)
li2
all.equal(ylin1,decomposition.y_cmp1)
# la decomposition est faite en log et remise en niveau 
# sa : là on devrait voir si correction biais 
sa_d <-round(exp(decomposition.sa_lin1)-decomposition.sa_cmp1,6)
sa_d

# biais

# t : là on devrait voir si correction biais (remise)
t_d <-round(exp(decomposition.t_lin1)-decomposition.t_cmp1,6)
t_d

# s : là on devrait voir si correction biais moyenne à 1 ?
s_d <-round(exp(decomposition.s_lin1)-decomposition.s_cmp1,6)
s_d
# rounding for non integer periods
nc<-round(length(y)-length(y)%%12)
nc
mean(decomposition.s_lin1[1:nc])
mean(exp(decomposition.s_lin1)[1:nc])
mean(decomposition.s_cmp1[1:nc])

# i : là on devrait voir si correction biais moyenne à 1 ?
i_d <-round(exp(decomposition.i_lin1)-decomposition.i_cmp1,6)
i_d
mean(decomposition.i_lin1)
mean(exp(decomposition.i_lin1))
mean(decomposition.i_cmp1) # a ete corrigé 

### on veut mean (ylin)= mean (sa_lin)
mean(ylin)
mean(decomposition.sa_cmp)
# petit ecart 
plot(y)
## GROS pb aucune difference de resultat


 
## verif realloc components (doc)

```



### issue 1: modes x11 

### issue 2: v sigmas 




################ set X11 spec: how to create one
# FILE : set_X11_spec.R
#' Set X-11 Specification

# need 1 create a sheer X11 customized spec, default spec = spec_x11() : OK ?
# TO DO :make clearer the difference of "X11" and other predifined x13 specs "RSA5"

# need 2 : customize the x11 part of an X13 spec: MET ?
# spec de depart = "RSA5c" pex

## pb pas le choix "X11" dans default spec : voir RegARIMA/X-13 Default Specification

#' @param bias TODO.: voir code JP pour tramo
#'
# example to be added (add spec creation code )

# modif 1

## param : seasonal.filter pas terrible, car ça peut etre le meme pour toute la série mais pas Msr

# modif 2

#' @param sigma.vector a vector to specify one of the two groups of periods for which standard errors used for extreme values
#' detection and adjustment will be computed separately.

# Modif 3
#' @param x the specification to be modified, default X11 spec can be be obtained as 'x=spec_x11()'

### Test
# set_x11 <- function(x,
#                     mode = c(NA, "Undefined", "Additive", "Multiplicative", "LogAdditive", "PseudoAdditive"),
#                     seasonal.comp = NA,
#                     seasonal.filter = NA,
#                     henderson.filter = NA,
#                     lsigma = NA,
#                     usigma = NA,
#                     fcasts = NA,
#                     bcasts = NA,
#                     calendar.sigma = c(NA, "None", "Signif", "All", "Select"),
#                     sigma.vector = NA,
#                     exclude.forecast = NA,
#                     bias = c(NA, "LEGACY"))

init_spec <- spec_x11()
# issue
new_spec <- set_x11(
    init_spec,
    mode = "LogAdditive",
    seasonal.comp = 1,
    seasonal.filter = "S3X9",

    # c("S3X3","S3X3","S3X3","S3X3","S3X3","S3X3",
    #                 "S3X3","S3X3","S3X3","S3X3","S3X5","S3X9"),
    # issue si vecteur length 4 or 12
    henderson.filter = 0,
    lsigma = 1.7,
    usigma = 2.7,
    fcasts = -1,
    bcasts = -1,
    calendar.sigma = "Select",
    sigma.vector = c(1, 2, 2, 1),
    exclude.forecast = FALSE,
    bias = "LEGACY"
)
new_spec

# TEST need 2 : customize the x11 part of an X13 spec: MET ?
# spec de depart = "RSA5c" pex
# issue
# ok ça marche, mais par exemple va modifier e
### obj ; explique ce qui n' pas

init_spec <- x13_spec()
init_spec
# issue : seasonal filter and sigma vector
new_spec <- set_x11(
    init_spec,
    mode = "LogAdditive",
    seasonal.comp = 1,
    seasonal.filter = "S3X9",

    # c("S3X3","S3X3","S3X3","S3X3","S3X3","S3X3",
    #                 "S3X3","S3X3","S3X3","S3X3","S3X5","S3X9"),
    # issue si vecteur length 4 or 12
    henderson.filter = 7,
    lsigma = 1.7,
    usigma = 2.7,
    fcasts = -1,
    bcasts = -1,
    calendar.sigma = "All",
    sigma.vector = NA,
    exclude.forecast = FALSE,
    bias = "LEGACY"
)
new_spec

# modif X11 params dans une spec X13 (ds rjd3toolkit) ?

################ set X13 spec: how to create one
# FILE n°3 : X13_spec.R
## homogeneisation noms spec
#' @rdname x13_spec @rdname x13_spec
#'
#' quels sont les specs par defaut

s <- spec_x11()
s
s1 <- spec_regarima()
s1 # RG2c ??

s2 <- x13_spec()
s2 # RSA2c ??

### issue faut il un nom de spec ou un spec object amibgu
# nom ambigu des examples ente specs regarima et specs X13 (même si tout marche)
## spec object useful for mofis
sp <- x13_spec("rg5c")
y <- rjd3toolkit::ABS$X0.2.09.10.M
fast_x13(y, spec = "rsa5c") # works
x13(y, spec = "rsa5c") # works ok but issue = no print ? or no automatic print ?
sp <- rjd3toolkit::add_outlier(
    sp,
    type = c("AO"),
    c("2015-01-01", "2010-01-01")
)
sp <- rjd3toolkit::set_transform(
    rjd3toolkit::set_tradingdays(
        rjd3toolkit::set_easter(sp, enabled = FALSE),
        option = "workingdays"
    ),
    fun = "None"
)
sp <- set_x11(sp, henderson.filter = 13)
fast_x13(y, spec = sp)

### pb =  modif de la spec et notamment de la partie x11

# In the estimation functions you can diectly use a specification name (string)
y <- rjd3toolkit::ABS$X0.2.09.10.M
fast_x13(y, "rsa3")
x13(y, "rsa5c") # issue: no print
fast_regarima(y, "rg0") # print exists
regarima(y, "rg3") # issue: no print
#'
#' If you want to customize a specification you have to create a specification object first
sp <- x13_spec("rsa5c")
sp <- rjd3toolkit::add_outlier(
    sp,
    type = c("AO"),
    c("2015-01-01", "2010-01-01")
)
# sp <-  rjd3toolkit::set_transform(
#'    rjd3toolkit::set_tradingdays(
#'      rjd3toolkit::set_easter(sp, enabled = FALSE),
#'     option = "workingdays"
#'   ),
#'   fun = "None"
#' )
x13(y, spec = sp)
sp <- set_x11(sp, henderson.filter = 13)
fast_x13(y, spec = sp)

################ set X13 spec: how to create one
# FILE n°3 : udvar.R

# retrieve names = bof : redefine explanation

userdefined_variables_x13("x13")
#' userdefined_variables_x13("regarima")
#' userdefined_variables_x13("x11")
################ ISSUE ?
y <- rjd3toolkit::ABS$X0.2.09.10.M
m <- x13(y, "rsa5c", userdefined = c("decomposition.b20", "ycal"))
m$user_defined$decomposition.b20
# Error in .jcall(jx, out_class, "getResult") :
#     method getResult with signature ()Ljdplus/x13/X13Results; not found

m$user_defined$b20
m$user_defined$cal
m$user_defined$residuals.kurtosis


m <- x13(y, "rsa3", userdefined = c("b20"))
m
m$user_defined$b20

### mode specific issues

#### set arima
## pre-condition
# ## automodel
x13_spec_d$regarima$automodel$enabled
sa_x13_d$estimation_spec$regarima$automodel$enabled
sa_x13_d$result_spec$regarima$automodel$enabled


# #
x13_spec_d$regarima$arima$d
sa_x13_d$estimation_spec$regarima$arima$d
sa_x13_d$result_spec$regarima$arima$d

#
x13_spec_d$regarima$arima$bd
sa_x13_d$estimation_spec$regarima$arima$bd
sa_x13_d$result_spec$regarima$arima$bd


x13_spec_d$regarima$arima$phi
sa_x13_d$estimation_spec$regarima$arima$phi
sa_x13_d$result_spec$regarima$arima$phi


x13_spec_d$regarima$arima$theta
sa_x13_d$estimation_spec$regarima$arima$theta
sa_x13_d$result_spec$regarima$arima$theta

x13_spec_d$regarima$arima$bphi
sa_x13_d$estimation_spec$regarima$arima$bphi
sa_x13_d$result_spec$regarima$arima$bphi


x13_spec_d$regarima$arima$btheta
sa_x13_d$estimation_spec$regarima$arima$btheta
sa_x13_d$result_spec$regarima$arima$btheta


