---
title: "T-rjd3x13 Dico et Output"
format: html
---

```{r}
#| label: loading-rjdverse
#| echo: true
#| eval: true
library("rjd3toolkit")
library("rjd3x13")
```

### Issues and Mails 

JP : spectral peaks TD ref issue Markus 
Mail ?

keep it all in this file 

### Prints (voir T, july TP)

- model span in print summary 


### Full dico objects

Questions 
- all relevant to x13 ?

```{r}


### Dictionnaries x13, ts, toolkit
library(rjd3toolkit)
library(rjd3x13)
library(rjd3tramoseats)
library(xlsx)

a <- rjd3x13::x13_full_dictionary() |> as.data.frame()
write.xlsx(a, "x13dico.xlsx")

str(a)
View(a)
b <- rjd3tramoseats::tramoseats_full_dictionary() |> as.data.frame()
write.xlsx(b, "TSdico.xlsx")


```


### Parallel avec GUI 

same data specs 

### Create "rich" x13 model 

remplir completement la spec 
- alloc to comps: plus riche

Obj: doc str(model) as well and comp with GUI display 


```{r}

## Import des données ----------------------------------------------------------

# Données CSV
# ipi <- read.csv2(file.path("Data", "IPI_nace4.csv"))

ipi <- read.csv2("data/IPI_nace4.csv")
str(ipi)
# obj comp avec GUI 

ipi$DATE <- as.Date(ipi$date, format = "%d/%m/%Y") # careful on date spelling
ipi[, -1] <- sapply(ipi[, -1], as.numeric)
View(ipi)

# # Donnees excel
# ipi_nace4_ind <- read.xlsx(
#     file.path("V:", "Formations-Stats", "CVS-CJO", "Donnees", "IPI_nace4_ind.xlsx"),
#     detectDates = TRUE, sheet = 1L
# )
# ipi_nace4_ind$date <- as.Date(ipi_nace4_ind$date)
# # View(ipi_nace4_ind)

# # Visualisation de la série
# ipi[1, "RF3030"]


## Manipulation des données ----------------------------------------------------

# Création d'un objet ts
y_raw <- ts(
    ipi[, "RF3030"],
    frequency = 12,
    start = c(1990, 1),
    end = c(2024, 1)
)
y_raw[1]
length(y_raw)

# Creating calendar regressors from a calendar

# Step 1: Create national (or other see doc) calendar if needed

# French calendar
french_calendar <- national_calendar(
    days = list(
        fixed_day(7, 14), # Bastille Day
        fixed_day(5, 8, validity = list(start = "1982-05-08")), # End of 2nd WW
        special_day("NEWYEAR"),
        special_day("CHRISTMAS"),
        special_day("MAYDAY"),
        special_day("EASTERMONDAY"),
        special_day("ASCENSION"),
        special_day("WHITMONDAY"),
        special_day("ASSUMPTION"),
        special_day("ALLSAINTSDAY"),
        special_day("ARMISTICE")
    )
)


### Step 2: Create regressors

# Create set of (6) regressors every day is different, contrast with Sunday,
# based on french national calendar
regs_td <- rjd3toolkit::calendar_td(
    calendar = french_calendar,
    # formats the regressor like your raw series (length, frequency..)
    s = y_raw,
    groups = c(1, 2, 3, 4, 5, 6, 0),
    contrasts = TRUE
)

# create an intervention variable (to be allocated to "trend")
iv1 <- intervention_variable(
    s = y_raw,
    starts = "2015-01-01",
    ends = "2015-12-01"
)


# regressors can be any TS object

#  Step 3: Create a modelling context

# Gather regressors into a list
my_regressors <- list(
    Monday = regs_td[, 1],
    Tuesday = regs_td[, 2],
    Wednesday = regs_td[, 3],
    Thursday = regs_td[, 4],
    Friday = regs_td[, 5],
    Saturday = regs_td[, 6],
    reg1 = iv1
)

# create modelling context
my_context <- modelling_context(variables = my_regressors)
# check variables present in modelling context
rjd3toolkit::.r2jd_modellingcontext(my_context)$getTsVariableDictionary()


### Step 4: Add regressors to specification

x13_spec <- rjd3x13::x13_spec("rsa3")
# x13_spec_user_defined<- rjd3x13::x13_spec("rsa3")
x13_spec_user_defined <- rjd3toolkit::set_tradingdays(
    x = x13_spec,
    option = "UserDefined",
    uservariable = c(
        "r.Monday",
        "r.Tuesday",
        "r.Wednesday",
        "r.Thursday",
        "r.Friday",
        "r.Saturday"
    ),
    test = "None"
)

  # autoadjust = NA,
  # leapyear = c(NA, "LeapYear", "LengthOfPeriod", "None"),
  # leapyear.coef = NA,
  # leapyear.coef.type = c(NA, "Fixed", "Estimated")

x13_spec_user_defined$regarima$regression$td$lp
x13_spec_user_defined$regarima$regression$td$td


# step 5: define user defined output 
ud<-rjd3x13::x13_dictionary()

# add intervention variable to spec, choosing the component to allocate
# the effects to TREND
x13_spec_user_defined <- add_usrdefvar(
    x = x13_spec_user_defined,
    group = "r",
    name = "reg1",
    label = "iv1",
    regeffect = "Trend"
)

x13_spec_user_defined$regarima$regression$users

# Step 6: Estimate with context and user-defined output 

sa_x13_ud <- rjd3x13::x13(y_raw, x13_spec_user_defined, context = my_context, userdefined = ud)

x13_spec_user_defined$regarima$regression$td$td # NONE ?

```


### Specs for tests

keep the same final model name for practicity of navigating UD output

```{r}
## 1 model span

x13_spec_user_defined<- set_estimate(
    x13_spec_user_defined,
    type = "From",
    d0 = "2012-01-01")
sa_x13_ud <- rjd3x13::x13(y_raw, x13_spec_user_defined, context = my_context, userdefined = ud)

y_raw_model<-window(y_raw, start=c(2012,1))
length(y_raw_model)

x13_spec_user_defined$regarima$estimate$span$d0


## log and LY

x13_spec_user_defined <- set_transform(
 x13_spec_user_defined,
  fun = "Log",
  adjust = "LeapYear",
  outliers = TRUE
)

sa_x13_ud <- rjd3x13::x13(y_raw, x13_spec_user_defined, context = my_context, userdefined = ud)

x13_spec_user_defined$regarima$transform$adjust # adjust ex ante

x13_spec_user_defined$regarima$regression$td$lp # regresseur NONE

## add bench

x13_spec_user_defined<- set_benchmarking(
  x13_spec_user_defined,
     enabled = TRUE,
    target = "Original",
    rho = 0.8,
    lambda = 0.5,
    forecast = FALSE,
    bias = "None")
sa_x13_ud <- rjd3x13::x13(y_raw, x13_spec_user_defined, context = my_context, userdefined = ud)

## check  
  # enabled = NA,
  # target = c(NA, "CalendarAdjusted", "Original"),
  # rho = NA,
  # lambda = NA,
  # forecast = NA,
  # bias = c("None", "Additive", "Multiplicative")



## add easter

x13_spec_user_defined <- set_easter(
  x13_spec_user_defined,
  enabled = TRUE,
  julian = TRUE,
  duration = 8
)
  # 
  # test = c(NA, "Add", "Remove", "None"),
  # coef = NA,
  # coef.type = c(NA, "Estimated", "Fixed"),
  # type = c(NA, "Unused", "Standard", "IncludeEaster", "IncludeEasterMonday")


sa_x13_ud <- rjd3x13::x13(y_raw, x13_spec_user_defined, context = my_context, userdefined = ud)

### ADD missing values : PB estimation with missing values 

y_raw[c(32,75,111,254,321)]<-NA #5
y_raw


# Création d'un objet ts
y_raw <- ts(
    ipi[, "RF3030"],
    frequency = 12,
    start = c(1990, 1),
    end = c(2024, 1)
)
y_raw[1]
length(y_raw)

sa_x13_ud <- rjd3x13::x13(y_raw, x13_spec_user_defined, context = my_context, userdefined = ud)

### REESITIMATION : TUILE if missing values 
sa_x13_ud <- rjd3x13::x13(y_raw, x13_spec_user_defined, context = my_context, userdefined = ud)

## 2 obj test non user def td 


```



#### Navigating spec 

```{r}
str(x13_spec_user_defined)
x13_spec_user_defined$regarima$regression$td$lp

```



### generate reading of ud output 

```{r, eval=FALSE}

n <- length(ud)
n
for (i in 1:n){
print(sprintf("sa_x13_ud$user_defined$%s", ud[i]))
}
```

### check output and comment 

Reperer là ou rien de généré à tort ou erreur 

- span


#### series (1st focus)

```{r}

summary(sa_x13_ud)
str(sa_x13_ud)

sa_x13_ud$user_defined$period
sa_x13_ud$user_defined$span.start
sa_x13_ud$user_defined$span.end
sa_x13_ud$user_defined$span.n
sa_x13_ud$user_defined$span.missing
sa_x13_ud$user_defined$log
sa_x13_ud$user_defined$adjust




sa_x13_ud$user_defined$likelihood.ll
sa_x13_ud$user_defined$likelihood.adjustedll
sa_x13_ud$user_defined$likelihood.ssqerr
sa_x13_ud$user_defined$likelihood.aic
sa_x13_ud$user_defined$likelihood.aicc
#a clarifier 
sa_x13_ud$user_defined$likelihood.bic
sa_x13_ud$user_defined$likelihood.bicc
sa_x13_ud$user_defined$likelihood.bic2

sa_x13_ud$user_defined$likelihood.hannanquinn

# savoir deduire les resultats
sa_x13_ud$user_defined$likelihood.nparams
sa_x13_ud$user_defined$likelihood.nobs
sa_x13_ud$user_defined$likelihood.neffectiveobs
sa_x13_ud$user_defined$likelihood.df
sa_x13_ud$user_defined$arima.p
sa_x13_ud$user_defined$arima.d
sa_x13_ud$user_defined$arima.q
sa_x13_ud$user_defined$arima.bp
sa_x13_ud$user_defined$arima.bd
sa_x13_ud$user_defined$arima.bq
sa_x13_ud$user_defined$arima.theta # format
## coeff + std E + T stat: named matrix
class(sa_x13_ud$user_defined$arima.theta)
sa_x13_ud$user_defined$arima.theta[1,1]

sa_x13_ud$user_defined$arima.phi
sa_x13_ud$user_defined$arima.btheta
sa_x13_ud$user_defined$arima.bphi

### model psan OK
sa_x13_ud$user_defined$regression.espan.start
sa_x13_ud$user_defined$regression.espan.end
sa_x13_ud$user_defined$regression.espan.n
sa_x13_ud$user_defined$regression.espan.missing

## here methodo clarifications
sa_x13_ud$user_defined$regression.mean
sa_x13_ud$user_defined$regression.nlp
sa_x13_ud$user_defined$regression.ntd # number of trading day regressors user-defined or not ?

### TUILE ici
sa_x13_ud$user_defined$regression.leaster
sa_x13_ud$user_defined$regression.nmh


sa_x13_ud$user_defined$regression.nout
sa_x13_ud$user_defined$regression.nao
sa_x13_ud$user_defined$regression.nls
sa_x13_ud$user_defined$regression.ntc
sa_x13_ud$user_defined$regression.nso
sa_x13_ud$user_defined$regression.nusers # user defined vars : how is 
## how is tis counted 

sa_x13_ud$user_defined$regression.mu

sa_x13_ud$user_defined$regression.lp
sa_x13_ud$user_defined$regression.td # NULL alors que td ds la spec : non user-defined 

sa_x13_ud$user_defined$regression.td-derived # introuvable
sa_x13_ud$user_defined$regression.td-ftest # introuvable
sa_x13_ud$user_defined$
sa_x13_ud$user_defined$regression.easter
sa_x13_ud$user_defined$regression.outlier # contents ? pb = que 1 oulier ?
sa_x13_ud$user_defined$regression.user
sa_x13_ud$user_defined$regression.missing # 
class(sa_x13_ud$user_defined$arima.theta)
sa_x13_ud$user_defined$arima.theta[1,1]
sa_x13_ud$user_defined$arima.theta[1,2]
sa_x13_ud$user_defined$arima.theta[1,3]
sa_x13_ud$user_defined$arima.theta[1,4]

sa_x13_ud$user_defined$arima.theta[2,1] # rien sur 2eme missing value 
sa_x13_ud$user_defined$residuals.res
length(sa_x13_ud$user_defined$residuals.res)
sa_x13_ud$user_defined$residuals.tsres
length(sa_x13_ud$user_defined$residuals.tsres)
sa_x13_ud$user_defined$residuals.n
sa_x13_ud$user_defined$residuals.df
sa_x13_ud$user_defined$residuals.dfc
sa_x13_ud$user_defined$residuals.ser
sa_x13_ud$user_defined$residuals.ser_ml
sa_x13_ud$user_defined$residuals.type
sa_x13_ud$user_defined$residuals.mean
sa_x13_ud$user_defined$residuals.skewness
sa_x13_ud$user_defined$residuals.kurtosis
sa_x13_ud$user_defined$residuals.doornikhansen
sa_x13_ud$user_defined$residuals.lb
sa_x13_ud$user_defined$residuals.bp
sa_x13_ud$user_defined$residuals.lb2
sa_x13_ud$user_defined$residuals.bp2
sa_x13_ud$user_defined$residuals.seaslb
sa_x13_ud$user_defined$residuals.seasbp
sa_x13_ud$user_defined$residuals.nruns
sa_x13_ud$user_defined$residuals.lruns
sa_x13_ud$user_defined$residuals.nudruns
sa_x13_ud$user_defined$residuals.ludruns
sa_x13_ud$user_defined$regression.ml.parameters
sa_x13_ud$user_defined$regression.ml.pcovar
sa_x13_ud$user_defined$regression.ml.pcovar-ml
sa_x13_ud$user_defined$regression.ml.pcorr
sa_x13_ud$user_defined$regression.ml.pscore
sa_x13_ud$user_defined$regression.details.description
sa_x13_ud$user_defined$regression.details.type
sa_x13_ud$user_defined$regression.details.coefficients
sa_x13_ud$user_defined$regression.details.covar
sa_x13_ud$user_defined$regression.details.covar-ml #introuvable 

sa_x13_ud$user_defined$y
sa_x13_ud$user_defined$y_f
sa_x13_ud$user_defined$y_ef
sa_x13_ud$user_defined$y_b
sa_x13_ud$user_defined$y_eb
sa_x13_ud$user_defined$yc
sa_x13_ud$user_defined$yc_f
sa_x13_ud$user_defined$yc_b
sa_x13_ud$user_defined$ylin
sa_x13_ud$user_defined$ylin_f
sa_x13_ud$user_defined$ylin_b
sa_x13_ud$user_defined$det
sa_x13_ud$user_defined$det_f
sa_x13_ud$user_defined$det_b
sa_x13_ud$user_defined$cal
sa_x13_ud$user_defined$cal_f # pb car à 1 check GUI 
sa_x13_ud$user_defined$cal_b
sa_x13_ud$user_defined$ycal
sa_x13_ud$user_defined$ycal_f
sa_x13_ud$user_defined$ycal_b
sa_x13_ud$user_defined$tde
sa_x13_ud$user_defined$tde_f
sa_x13_ud$user_defined$tde_b
sa_x13_ud$user_defined$ee
sa_x13_ud$user_defined$ee_f
sa_x13_ud$user_defined$ee_b
sa_x13_ud$user_defined$omhe
sa_x13_ud$user_defined$omhe_f
sa_x13_ud$user_defined$omhe_b
sa_x13_ud$user_defined$mhe
sa_x13_ud$user_defined$mhe_f
sa_x13_ud$user_defined$mhe_b
sa_x13_ud$user_defined$out
sa_x13_ud$user_defined$out_f
sa_x13_ud$user_defined$out_b
sa_x13_ud$user_defined$reg
sa_x13_ud$user_defined$reg_f
sa_x13_ud$user_defined$reg_b
sa_x13_ud$user_defined$l
sa_x13_ud$user_defined$l_f
sa_x13_ud$user_defined$l_b
sa_x13_ud$user_defined$full_res
sa_x13_ud$user_defined$mode
sa_x13_ud$user_defined$seasonal
sa_x13_ud$user_defined$sa
sa_x13_ud$user_defined$t
sa_x13_ud$user_defined$s
sa_x13_ud$user_defined$i
sa_x13_ud$user_defined$sa_f
sa_x13_ud$user_defined$t_f
sa_x13_ud$user_defined$s_f
sa_x13_ud$user_defined$i_f
sa_x13_ud$user_defined$out_t
sa_x13_ud$user_defined$out_s
sa_x13_ud$user_defined$out_i
sa_x13_ud$user_defined$reg_t
sa_x13_ud$user_defined$reg_s
sa_x13_ud$user_defined$reg_i
sa_x13_ud$user_defined$reg_sa
sa_x13_ud$user_defined$reg_u
sa_x13_ud$user_defined$reg_y
sa_x13_ud$user_defined$det_t
sa_x13_ud$user_defined$det_s
sa_x13_ud$user_defined$det_i
sa_x13_ud$user_defined$out_t_f
sa_x13_ud$user_defined$out_s_f
sa_x13_ud$user_defined$out_i_f
## check allocation 
sa_x13_ud$user_defined$reg_t_f
sa_x13_ud$user_defined$reg_s_f
sa_x13_ud$user_defined$reg_i_f
sa_x13_ud$user_defined$reg_sa_f
sa_x13_ud$user_defined$reg_u_f
sa_x13_ud$user_defined$reg_y_f
sa_x13_ud$user_defined$det_t_f
sa_x13_ud$user_defined$det_s_f
sa_x13_ud$user_defined$det_i_f
sa_x13_ud$user_defined$out_t_b
sa_x13_ud$user_defined$out_s_b
sa_x13_ud$user_defined$out_i_b
sa_x13_ud$user_defined$reg_t_b
sa_x13_ud$user_defined$reg_s_b
sa_x13_ud$user_defined$reg_i_b
sa_x13_ud$user_defined$reg_sa_b
sa_x13_ud$user_defined$reg_u_b
sa_x13_ud$user_defined$reg_y_b
sa_x13_ud$user_defined$det_t_b
sa_x13_ud$user_defined$det_s_b
sa_x13_ud$user_defined$det_i_b
## redef cf TEST 
sa_x13_ud$user_defined$decomposition.y_cmp
sa_x13_ud$user_defined$decomposition.y_cmp_f
sa_x13_ud$user_defined$decomposition.y_cmp_b
sa_x13_ud$user_defined$decomposition.sa_cmp
sa_x13_ud$user_defined$decomposition.t_cmp
sa_x13_ud$user_defined$decomposition.s_cmp
sa_x13_ud$user_defined$decomposition.i_cmp
## end test
sa_x13_ud$user_defined$preadjustment.a1
sa_x13_ud$user_defined$preadjustment.a1a
sa_x13_ud$user_defined$preadjustment.a1b # backcast ? 
sa_x13_ud$user_defined$preadjustment.a6
sa_x13_ud$user_defined$preadjustment.a7
sa_x13_ud$user_defined$preadjustment.a8
### reallocations stored for final componenet computations ?
sa_x13_ud$user_defined$preadjustment.a8t
sa_x13_ud$user_defined$preadjustment.a8i
sa_x13_ud$user_defined$preadjustment.a8s
sa_x13_ud$user_defined$preadjustment.a9
sa_x13_ud$user_defined$preadjustment.a9
sa_x13_ud$user_defined$preadjustment.a9cal
sa_x13_ud$user_defined$preadjustment.a9u
sa_x13_ud$user_defined$preadjustment.a9sa
sa_x13_ud$user_defined$preadjustment.a9ser
sa_x13_ud$user_defined$decomposition.b1
sa_x13_ud$user_defined$decomposition.b2
sa_x13_ud$user_defined$decomposition.b3
sa_x13_ud$user_defined$decomposition.b4
sa_x13_ud$user_defined$decomposition.b5
sa_x13_ud$user_defined$decomposition.b6
sa_x13_ud$user_defined$decomposition.b7
sa_x13_ud$user_defined$decomposition.b8
sa_x13_ud$user_defined$decomposition.b9
sa_x13_ud$user_defined$decomposition.b10
sa_x13_ud$user_defined$decomposition.b11
sa_x13_ud$user_defined$decomposition.b13
sa_x13_ud$user_defined$decomposition.b17
sa_x13_ud$user_defined$decomposition.b20
sa_x13_ud$user_defined$decomposition.c1
sa_x13_ud$user_defined$decomposition.c2
sa_x13_ud$user_defined$decomposition.c4
sa_x13_ud$user_defined$decomposition.c5
sa_x13_ud$user_defined$decomposition.c6
sa_x13_ud$user_defined$decomposition.c7
sa_x13_ud$user_defined$decomposition.c9
sa_x13_ud$user_defined$decomposition.c10
sa_x13_ud$user_defined$decomposition.c11
sa_x13_ud$user_defined$decomposition.c13
sa_x13_ud$user_defined$decomposition.c17
sa_x13_ud$user_defined$decomposition.c20
sa_x13_ud$user_defined$decomposition.d1
sa_x13_ud$user_defined$decomposition.d2
sa_x13_ud$user_defined$decomposition.d4
sa_x13_ud$user_defined$decomposition.d5
sa_x13_ud$user_defined$decomposition.d6
sa_x13_ud$user_defined$decomposition.d7
sa_x13_ud$user_defined$decomposition.d8
sa_x13_ud$user_defined$decomposition.d9
sa_x13_ud$user_defined$decomposition.d10
sa_x13_ud$user_defined$decomposition.d11
sa_x13_ud$user_defined$decomposition.d12
sa_x13_ud$user_defined$decomposition.d13
sa_x13_ud$user_defined$decomposition.x11-all # pb !!
sa_x13_ud$user_defined$decomposition.icratio
sa_x13_ud$user_defined$decomposition.trend-filter # pb 
sa_x13_ud$user_defined$decomposition.seasonal-filters  # pb 
sa_x13_ud$user_defined$decomposition.d9-global-msr  # pb 
sa_x13_ud$user_defined$decomposition.d9-msr  # pb 
sa_x13_ud$user_defined$decomposition.d9-msr-table  # pb 
sa_x13_ud$user_defined$finals.d11
sa_x13_ud$user_defined$finals.d12
sa_x13_ud$user_defined$finals.d13
sa_x13_ud$user_defined$finals.d16
sa_x13_ud$user_defined$finals.d18
sa_x13_ud$user_defined$finals.d11a
sa_x13_ud$user_defined$finals.d12a
sa_x13_ud$user_defined$finals.d16a
sa_x13_ud$user_defined$finals.d18a
sa_x13_ud$user_defined$finals.d11b
sa_x13_ud$user_defined$finals.d12b
sa_x13_ud$user_defined$finals.d16b
sa_x13_ud$user_defined$finals.d18b
sa_x13_ud$user_defined$finals.e1
sa_x13_ud$user_defined$finals.e2
sa_x13_ud$user_defined$finals.e3
sa_x13_ud$user_defined$finals.e11
# pb not generated: mauvais ecriture, missing param : missing `` (TRAP°)
sa_x13_ud$user_defined$`diagnostics.seas-lin-combined`
sa_x13_ud$user_defined$`diagnostics.seas-lin-evolutive`
sa_x13_ud$user_defined$`diagnostics.seas-lin-stable` 
sa_x13_ud$user_defined$`diagnostics.seas-si-combined`
sa_x13_ud$user_defined$`diagnostics.seas-si-combined3`
sa_x13_ud$user_defined$`diagnostics.seas-si-evolutive`
sa_x13_ud$user_defined$`diagnostics.seas-si-stable`
sa_x13_ud$user_defined$`diagnostics.seas-res-combined`
sa_x13_ud$user_defined$`diagnostics.seas-res-combined3`
sa_x13_ud$user_defined$`diagnostics.seas-res-evolutive`
sa_x13_ud$user_defined$`diagnostics.seas-res-stable`
sa_x13_ud$user_defined$`diagnostics.seas-sa-combined`
sa_x13_ud$user_defined$`diagnostics.seas-sa-combined3`
sa_x13_ud$user_defined$`diagnostics.seas-sa-evolutive`
sa_x13_ud$user_defined$`diagnostics.seas-sa-stable`
sa_x13_ud$user_defined$`diagnostics.seas-i-combined`
sa_x13_ud$user_defined$`diagnostics.seas-i-combined3`
sa_x13_ud$user_defined$`diagnostics.seas-i-evolutive`
sa_x13_ud$user_defined$`diagnostics.seas-i-stable`
sa_x13_ud$user_defined$`diagnostics.seas-lin-qs`
sa_x13_ud$user_defined$`diagnostics.seas-lin-f`
sa_x13_ud$user_defined$`diagnostics.seas-lin-friedman`
sa_x13_ud$user_defined$`diagnostics.seas-lin-kw`
sa_x13_ud$user_defined$`diagnostics.seas-lin-periodogram`
sa_x13_ud$user_defined$`diagnostics.seas-lin-spectralpeaks`
sa_x13_ud$user_defined$`diagnostics.seas-res-qs`
sa_x13_ud$user_defined$`diagnostics.seas-res-f`
sa_x13_ud$user_defined$`diagnostics.seas-res-friedman`
sa_x13_ud$user_defined$`diagnostics.seas-res-kw`
sa_x13_ud$user_defined$`diagnostics.seas-res-periodogram`
sa_x13_ud$user_defined$`diagnostics.seas-res-spectralpeaks`
sa_x13_ud$user_defined$`diagnostics.seas-sa-qs`
sa_x13_ud$user_defined$`diagnostics.seas-sa-f`
sa_x13_ud$user_defined$`diagnostics.seas-sa-friedman`
sa_x13_ud$user_defined$`diagnostics.seas-sa-kw`
sa_x13_ud$user_defined$`diagnostics.seas-sa-periodogram`
sa_x13_ud$user_defined$`diagnostics.seas-sa-spectralpeaks`
sa_x13_ud$user_defined$`diagnostics.seas-i-qs`
sa_x13_ud$user_defined$`diagnostics.seas-i-f`
sa_x13_ud$user_defined$`diagnostics.seas-i-friedman`
sa_x13_ud$user_defined$`diagnostics.seas-i-kw`
sa_x13_ud$user_defined$`diagnostics.seas-i-periodogram`
sa_x13_ud$user_defined$`diagnostics.seas-i-spectralpeaks`
sa_x13_ud$user_defined$`diagnostics.seas-sa-ac1`
sa_x13_ud$user_defined$`diagnostics.td-res-all`
sa_x13_ud$user_defined$`diagnostics.td-res-last`
sa_x13_ud$user_defined$`diagnostics.td-sa-all`
sa_x13_ud$user_defined$`diagnostics.td-sa-last`
sa_x13_ud$user_defined$`diagnostics.td-i-all`
sa_x13_ud$user_defined$`diagnostics.td-i-last`
sa_x13_ud$user_defined$`diagnostics.fcast-insample-mean`
sa_x13_ud$user_defined$`diagnostics.fcast-outsample-mean`
sa_x13_ud$user_defined$`diagnostics.fcast-outsample-variance`
sa_x13_ud$user_defined$`m-statistics.m1`
sa_x13_ud$user_defined$`m-statistics.m2`
sa_x13_ud$user_defined$`m-statistics.m3`
sa_x13_ud$user_defined$`m-statistics.m4`
sa_x13_ud$user_defined$`m-statistics.m5`
sa_x13_ud$user_defined$`m-statistics.m6`
sa_x13_ud$user_defined$`m-statistics.m7`
sa_x13_ud$user_defined$`m-statistics.m8`
sa_x13_ud$user_defined$`m-statistics.m9`
sa_x13_ud$user_defined$`m-statistics.m10`
sa_x13_ud$user_defined$`m-statistics.m11`
sa_x13_ud$user_defined$`m-statistics.q`
sa_x13_ud$user_defined$`m-statistics.q-m2` 
## end of generation pb 
sa_x13_ud$user_defined$variancedecomposition.cycle
sa_x13_ud$user_defined$variancedecomposition.seasonality
sa_x13_ud$user_defined$variancedecomposition.irregular
sa_x13_ud$user_defined$variancedecomposition.tdh
sa_x13_ud$user_defined$variancedecomposition.others
sa_x13_ud$user_defined$variancedecomposition.total

sa_x13_ud$user_defined$quality.summary


sa_x13_ud$user_defined$benchmarking.original
sa_x13_ud$user_defined$benchmarking.target
sa_x13_ud$user_defined$benchmarking.result

```

### spectral peaks issue Markus 

```{r}
# seasonal peaks on linearized series
sa_x13_ud$user_defined$`diagnostics.seas-lin-periodogram`
sa_x13_ud$user_defined$`diagnostics.seas-lin-spectralpeaks`
# seasonal peaks on reg-arima residuals
sa_x13_ud$user_defined$`diagnostics.seas-res-periodogram`
sa_x13_ud$user_defined$`diagnostics.seas-res-spectralpeaks`

# seasonal peaks on sa
sa_x13_ud$user_defined$`diagnostics.seas-sa-periodogram`
sa_x13_ud$user_defined$`diagnostics.seas-sa-spectralpeaks`

# seasonal peaks on i
sa_x13_ud$user_defined$`diagnostics.seas-i-periodogram`
sa_x13_ud$user_defined$`diagnostics.seas-i-spectralpeaks`



```



```{r}

library(dygraphs)
dygraph(sa_x13_ud$user_defined$full_res)

```


### Output questions (JP, KW)

- "untransformed" in the name...of the series: clarify 

### JP envoi 1

### Back log 

JP : spectral peaks TD ref issue Markus 
Mail ?

     .item(AtomicDictionary.Item.builder().name(D9_GLOBALMSR).description("global moving seasonality ratio on D9").outputClass(Double.class).build())
            .item(AtomicDictionary.Item.builder().name(D9_MSR).description("moving seasonality ratio on D9").outputClass(double[].class).build())
            .item(AtomicDictionary.Item.builder().name(D9_MSRTABLE).description("moving seasonality on D9 (details)").outputClass(Matrix.class).build())
            
or D

.item(AtomicDictionary.Item.builder().name(D9).description("Replacement Values for Extreme Seasonal-Irregular Values").outputClass(TsData.class).build())



.builder().name(DET).description("all deterministic effects (including pre-adjustment, but without trend polynomial effect)


FULL_RES="full_res" // full residuals. L^-1*([log]yc-[log]det)

pb transormed untransformed 

> sa_x13_ud$user_defined$adjust
[1] "None"
> sa_x13_ud$user_defined$likelihood.ll
[1] 433.6548
> sa_x13_ud$user_defined$likelihood.adjustedll
[1] -1376.78
> sa_x13_ud$user_defined$likelihood.ssqerr
[1] 2.445155
> sa_x13_ud$user_defined$likelihood.aic
[1] 2777.56
> sa_x13_ud$user_defined$likelihood.bic
[1] 2825.185
> sa_x13_ud$user_defined$likelihood.aicc
[1] 2778.386
> sa_x13_ud$user_defined$likelihood.bicc
[1] -4.906681
> sa_x13_ud$user_defined$likelihood.bic2
[1] -2.035
> sa_x13_ud$user_defined$likelihood.hannanquinn
[1] 2796.437

### STR spec comment 

> str(x13_spec_user_defined)
List of 3
 $ regarima    :List of 7
  ..$ basic     :List of 3
  .. ..$ span            :List of 5
  .. .. ..$ type: chr "ALL"
  .. .. ..$ d0  : NULL
  .. .. ..$ d1  : NULL
  .. .. ..$ n0  : int 0
  .. .. ..$ n1  : int 0
  .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. ..$ preprocessing   : logi TRUE
  .. ..$ preliminaryCheck: logi TRUE
  ..$ transform :List of 4
  .. ..$ fn      : chr "LOG"
  .. ..$ adjust  : chr "LEAPYEAR"
  .. ..$ aicdiff : num -2
  .. ..$ outliers: logi TRUE
  ..$ outlier   :List of 7
  .. ..$ outliers     :List of 3
  .. .. ..$ :List of 2
  .. .. .. ..$ type: chr "AO"
  .. .. .. ..$ va  : num 0
  .. .. ..$ :List of 2
  .. .. .. ..$ type: chr "LS"
  .. .. .. ..$ va  : num 0
  .. .. ..$ :List of 2
  .. .. .. ..$ type: chr "TC"
  .. .. .. ..$ va  : num 0
  .. ..$ span         :List of 5
  .. .. ..$ type: chr "ALL"
  .. .. ..$ d0  : NULL
  .. .. ..$ d1  : NULL
  .. .. ..$ n0  : int 0
  .. .. ..$ n1  : int 0
  .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. ..$ defva        : num 0
  .. ..$ method       : chr "ADDONE"
  .. ..$ monthlytcrate: num 0.7
  .. ..$ maxiter      : int 30
  .. ..$ lsrun        : int 0
  ..$ arima     :List of 7
  .. ..$ period: int 0
  .. ..$ d     : int 1
  .. ..$ bd    : int 1
  .. ..$ phi   : NULL
  .. ..$ theta :List of 2
  .. .. ..$ : num 0
  .. .. ..$ : chr "UNDEFINED"
  .. .. ..- attr(*, "dim")= int [1:2] 2 1
  .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. ..$ : NULL
  .. ..$ bphi  : NULL
  .. ..$ btheta:List of 2
  .. .. ..$ : num 0
  .. .. ..$ : chr "UNDEFINED"
  .. .. ..- attr(*, "dim")= int [1:2] 2 1
  .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. ..$ : NULL
  .. ..- attr(*, "class")= chr "JD3_SARIMA_ESTIMATION"
  ..$ automodel :List of 12
  .. ..$ enabled  : logi TRUE
  .. ..$ ljungbox : num 0.95
  .. ..$ tsig     : num 1
  .. ..$ predcv   : num 0.143
  .. ..$ ubfinal  : num 1.05
  .. ..$ ub1      : num 1.03
  .. ..$ ub2      : num 1.14
  .. ..$ cancel   : num 0.1
  .. ..$ fct      : num 1.01
  .. ..$ acceptdef: logi FALSE
  .. ..$ mixed    : logi TRUE
  .. ..$ balanced : logi FALSE
  ..$ regression:List of 8
  .. ..$ mean         : NULL
  .. ..$ check_mean   : logi FALSE
  .. ..$ td           :List of 12
  .. .. ..$ td            : chr "TD_NONE"
  .. .. ..$ lp            : chr "NONE"
  .. .. ..$ holidays      : chr ""
  .. .. ..$ users         : chr [1:6] "r.Monday" "r.Tuesday" "r.Wednesday" "r.Thursday" ...
  .. .. ..$ w             : int 0
  .. .. ..$ test          : chr "NO"
  .. .. ..$ auto          : chr "AUTO_NO"
  .. .. ..$ autoadjust    : logi FALSE
  .. .. ..$ tdcoefficients:List of 12
  .. .. .. ..$ : num 0
  .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. ..$ : num 0
  .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. ..$ : num 0
  .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. ..$ : num 0
  .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. ..$ : num 0
  .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. ..$ : num 0
  .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. ..- attr(*, "dim")= int [1:2] 2 6
  .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. ..$ : NULL
  .. .. ..$ lpcoefficient : NULL
  .. .. ..$ ptest1        : num 0
  .. .. ..$ ptest2        : num 0
  .. ..$ easter       :List of 4
  .. .. ..$ type       : chr "JULIAN"
  .. .. ..$ duration   : num 8
  .. .. ..$ test       : chr "NO"
  .. .. ..$ coefficient: NULL
  .. ..$ outliers     : NULL
  .. ..$ users        :List of 1
  .. .. ..$ :List of 5
  .. .. .. ..$ id       : chr "r.reg1"
  .. .. .. ..$ name     : chr "iv1"
  .. .. .. ..$ lag      : num 0
  .. .. .. ..$ coef     : NULL
  .. .. .. ..$ regeffect: chr "Trend"
  .. ..$ interventions: NULL
  .. ..$ ramps        : NULL
  ..$ estimate  :List of 2
  .. ..$ span:List of 5
  .. .. ..$ type: chr "FROM"
  .. .. ..$ d0  : chr "2012-01-01"
  .. .. ..$ d1  : NULL
  .. .. ..$ n0  : int 0
  .. .. ..$ n1  : int 0
  .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. ..$ tol : num 1e-07
  ..- attr(*, "class")= chr "JD3_REGARIMA_SPEC"
 $ x11         :List of 12
  ..$ mode         : chr "UNKNOWN"
  ..$ seasonal     : logi TRUE
  ..$ henderson    : int 0
  ..$ sfilters     : chr "FILTER_MSR"
  ..$ lsig         : num 1.5
  ..$ usig         : num 2.5
  ..$ nfcasts      : int -1
  ..$ nbcasts      : int 0
  ..$ sigma        : chr "NONE"
  ..$ vsigmas      : int(0) 
  ..$ excludefcasts: logi FALSE
  ..$ bias         : chr "RATIO"
  ..- attr(*, "class")= chr "JD3_X11_SPEC"
 $ benchmarking:List of 6
  ..$ enabled : logi TRUE
  ..$ target  : chr "TARGET_ORIGINAL"
  ..$ lambda  : num 0.5
  ..$ rho     : num 0.8
  ..$ bias    : chr "BIAS_NONE"
  ..$ forecast: logi FALSE
 - attr(*, "class")= chr "JD3_X13_SPEC"
 

### STR model commented 

fish out questions 


#### FULL
str(sa_x13_ud)
List of 4
 $ result         :List of 6
  ..$ preprocessing:List of 3
  .. ..$ description:List of 4
  .. .. ..$ log          : logi TRUE
  .. .. ..$ preadjustment: chr "LEAPYEAR"
  .. .. ..$ arima        :List of 7
  .. .. .. ..$ period: int 12
  .. .. .. ..$ d     : int 1
  .. .. .. ..$ bd    : int 1
  .. .. .. ..$ phi   : NULL
  .. .. .. ..$ theta :List of 2
  .. .. .. .. ..$ : num -0.771
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..- attr(*, "dim")= int [1:2] 2 1
  .. .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. .. ..$ : NULL
  .. .. .. ..$ bphi  : NULL
  .. .. .. ..$ btheta:List of 2
  .. .. .. .. ..$ : num -0.726
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..- attr(*, "dim")= int [1:2] 2 1
  .. .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. .. ..$ : NULL
  .. .. .. ..- attr(*, "class")= chr "JD3_SARIMA_ESTIMATION"
  .. .. ..$ variables    :List of 5
  .. .. .. ..$ :List of 3
  .. .. .. .. ..$ name: chr "iv1"
  .. .. .. .. ..$ type: chr "UNSPECIFIED"
  .. .. .. .. ..$ coef:'data.frame':	1 obs. of  2 variables:
  .. .. .. .. .. ..$ value: num -0.0436
  .. .. .. .. .. ..$ type : chr "ESTIMATED"
  .. .. .. ..$ :List of 3
  .. .. .. .. ..$ name: chr "usertd"
  .. .. .. .. ..$ type: chr "TD"
  .. .. .. .. ..$ coef:'data.frame':	6 obs. of  2 variables:
  .. .. .. .. .. ..$ value: num [1:6] -0.00786 0.01831 0.00349 0.01563 0.022 ...
  .. .. .. .. .. ..$ type : chr [1:6] "ESTIMATED" "ESTIMATED" "ESTIMATED" "ESTIMATED" ...
  .. .. .. ..$ :List of 3
  .. .. .. .. ..$ name: chr "easter"
  .. .. .. .. ..$ type: chr "EASTER"
  .. .. .. .. ..$ coef:'data.frame':	1 obs. of  2 variables:
  .. .. .. .. .. ..$ value: num -0.0633
  .. .. .. .. .. ..$ type : chr "ESTIMATED"
  .. .. .. ..$ :List of 3
  .. .. .. .. ..$ name: chr "TC (2020-03-01)"
  .. .. .. .. ..$ type: chr "TC"
  .. .. .. .. ..$ coef:'data.frame':	1 obs. of  2 variables:
  .. .. .. .. .. ..$ value: num -0.257
  .. .. .. .. .. ..$ type : chr "ESTIMATED"
  .. .. .. ..$ :List of 3
  .. .. .. .. ..$ name: chr "LS (2020-04-01)"
  .. .. .. .. ..$ type: chr "LS"
  .. .. .. .. ..$ coef:'data.frame':	1 obs. of  2 variables:
  .. .. .. .. .. ..$ value: num -0.448
  .. .. .. .. .. ..$ type : chr "ESTIMATED"
  .. ..$ estimation :List of 7
  .. .. ..$ y         : num [1:145] 4.82 4.79 5.02 4.81 4.75 ...
  .. .. ..$ X         : num [1:145, 1:10] 0 0 0 0 0 0 0 0 0 0 ...
  .. .. ..$ parameters:List of 4
  .. .. .. ..$ val        : num [1:2] -0.771 -0.726
  .. .. .. ..$ score      : num [1:2] 0.02026 -0.00422
  .. .. .. ..$ cov        : num [1:2, 1:2] 2.61e-03 -6.36e-05 -6.36e-05 1.13e-02
  .. .. .. ..$ description: chr "sarima (true signs)"
  .. .. ..$ b         : num [1:10] -0.04359 -0.00786 0.01831 0.00349 0.01563 ...
  .. .. ..$ bvar      : num [1:10, 1:10] 9.06e-04 1.80e-07 -1.21e-05 3.23e-05 -4.52e-05 ...
  .. .. ..$ likelihood:List of 10
  .. .. .. ..$ nobs         : int 145
  .. .. .. ..$ neffectiveobs: int 132
  .. .. .. ..$ nparams      : int 13
  .. .. .. ..$ ll           : num 158
  .. .. .. ..$ adjustedll   : num -487
  .. .. .. ..$ aic          : num 1000
  .. .. .. ..$ aicc         : num 1003
  .. .. .. ..$ bic          : num 1038
  .. .. .. ..$ bicc         : num -4.86
  .. .. .. ..$ ssq          : num 0.658
  .. .. .. ..- attr(*, "class")= chr "JD3_LIKELIHOOD"
  .. .. ..$ res       : num [1:132] 0.1298 -0.0698 0.0427 0.0719 0.1076 ...
  .. ..$ diagnostics:List of 14
  .. .. ..$ mean         :List of 2
  .. .. .. ..$ value : num -0.31
  .. .. .. ..$ pvalue: num 0.757
  .. .. .. ..- attr(*, "distribution")= chr "T with 132.0 degrees of freedom"
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ skewness     :List of 2
  .. .. .. ..$ value : num 0.183
  .. .. .. ..$ pvalue: num 0.392
  .. .. .. ..- attr(*, "distribution")= chr "Normal with Mean = 0.0 and Stdev = 0.21320071635561044"
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ kurtosis     :List of 2
  .. .. .. ..$ value : num 2.97
  .. .. .. ..$ pvalue: num 0.938
  .. .. .. ..- attr(*, "distribution")= chr "Normal with Mean = 3.0 and Stdev = 0.4264014327112209"
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ doornikhansen:List of 2
  .. .. .. ..$ value : num 0.825
  .. .. .. ..$ pvalue: num 0.662
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 2.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ lb           :List of 2
  .. .. .. ..$ value : num 24.2
  .. .. .. ..$ pvalue: num 0.337
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 22.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ bp           :List of 2
  .. .. .. ..$ value : num 22
  .. .. .. ..$ pvalue: num 0.461
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 22.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ seaslb       :List of 2
  .. .. .. ..$ value : num 0.295
  .. .. .. ..$ pvalue: num 0.863
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 2.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ seasbp       :List of 2
  .. .. .. ..$ value : num 0.26
  .. .. .. ..$ pvalue: num 0.878
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 2.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ lb2          :List of 2
  .. .. .. ..$ value : num 36.4
  .. .. .. ..$ pvalue: num 0.0275
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 22.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ bp2          :List of 2
  .. .. .. ..$ value : num 32.2
  .. .. .. ..$ pvalue: num 0.0747
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 22.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ nruns        :List of 2
  .. .. .. ..$ value : num 1.01
  .. .. .. ..$ pvalue: num 0.31
  .. .. .. ..- attr(*, "distribution")= chr "Normal with Mean = 0.0 and Stdev = 1.0"
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ lruns        :List of 2
  .. .. .. ..$ value : num 14.8
  .. .. .. ..$ pvalue: num 1
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 132.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ nudruns      :List of 2
  .. .. .. ..$ value : num 0.277
  .. .. .. ..$ pvalue: num 0.782
  .. .. .. ..- attr(*, "distribution")= chr "Normal with Mean = 0.0 and Stdev = 1.0"
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. .. ..$ ludruns      :List of 2
  .. .. .. ..$ value : num 1.66
  .. .. .. ..$ pvalue: num 1
  .. .. .. ..- attr(*, "distribution")= chr "Chi2 with 131.0 degrees of freedom "
  .. .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. ..- attr(*, "class")= chr "JD3_REGARIMA_RSLTS"
  ..$ preadjust    :List of 7
  .. ..$ a1 : Time-Series [1:409] from 1990 to 2024: 107.3 96.4 102.6 78.5 71.7 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ a1a: Time-Series [1:12] from 2024 to 2025: 121 135 128 112 142 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ a1b: NULL
  .. ..$ a6 : Time-Series [1:421] from 1990 to 2025: 1.022 0.991 1.022 0.958 1.013 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ a7 : Time-Series [1:421] from 1990 to 2025: 1 1 1.002 0.993 1.006 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ a8 : Time-Series [1:421] from 1990 to 2025: 1.56 1.56 1.56 1.56 1.56 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ a9 : Time-Series [1:421] from 1990 to 2025: 1 1 1 1 1 1 1 1 1 1 ...
  .. .. ..- attr(*, "name")= chr ""
  ..$ decomposition:List of 14
  .. ..$ d1             : Time-Series [1:421] from 1990 to 2025: 67.1 62.1 70.3 52.7 45 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d2             : Time-Series [1:409] from 1990 to 2024: 54.9 54.8 54.7 54.4 54.2 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d4             : Time-Series [1:409] from 1990 to 2024: 0.98 0.968 1.002 0.96 0.878 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d5             : Time-Series [1:421] from 1990 to 2025: 1.187 1.146 1.287 0.935 0.859 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d6             : Time-Series [1:421] from 1990 to 2025: 56.6 54.2 54.6 56.4 52.3 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d7             : Time-Series [1:421] from 1990 to 2025: 55 54.9 54.9 54.9 54.8 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d8             : Time-Series [1:421] from 1990 to 2025: 1.22 1.131 1.166 0.961 0.82 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d9             : Time-Series [1:421] from 1990 to 2025: NaN NaN 1.28 NaN NaN ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d10            : Time-Series [1:421] from 1990 to 2025: 1.196 1.143 1.287 0.944 0.851 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d11            : Time-Series [1:421] from 1990 to 2025: 56.1 54.4 49.8 55.8 52.8 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d12            : Time-Series [1:421] from 1990 to 2025: 54.8 54.8 54.8 54.8 54.7 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d13            : Time-Series [1:421] from 1990 to 2025: 1.024 0.992 0.909 1.02 0.965 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ final_seasonal : int 3
  .. ..$ final_henderson: int 23
  .. ..- attr(*, "class")= chr "JD3X11"
  ..$ final        :List of 13
  .. ..$ d11final: Time-Series [1:409] from 1990 to 2024: 87.8 85.1 77.9 87.4 82.6 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d12final: Time-Series [1:409] from 1990 to 2024: 85.8 85.7 85.7 85.7 85.7 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d13final: Time-Series [1:409] from 1990 to 2024: 1.024 0.992 0.909 1.02 0.965 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d16     : Time-Series [1:409] from 1990 to 2024: 1.222 1.133 1.317 0.898 0.867 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d18     : Time-Series [1:409] from 1990 to 2024: 1.022 0.991 1.024 0.951 1.019 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d11a    : Time-Series [1:12] from 2024 to 2025: 122 124 124 127 125 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d12a    : Time-Series [1:12] from 2024 to 2025: 124 124 125 125 126 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d16a    : Time-Series [1:12] from 2024 to 2025: 0.995 1.086 1.034 0.878 1.132 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ d18a    : Time-Series [1:12] from 2024 to 2025: 1.027 1.002 1.025 0.974 1 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ e1      : Time-Series [1:409] from 1990 to 2024: 107.3 96.4 112.9 78.5 71.7 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ e2      : Time-Series [1:409] from 1990 to 2024: 87.8 85.1 54.8 87.4 82.6 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ e3      : Time-Series [1:409] from 1990 to 2024: 1.024 0.992 1 1.02 0.965 ...
  .. .. ..- attr(*, "name")= chr ""
  .. ..$ e11     : Time-Series [1:409] from 1990 to 2024: 87.8 85.1 49.8 87.4 82.6 ...
  .. .. ..- attr(*, "name")= chr ""
  ..$ mstats       :List of 13
  .. ..$ m1 : num 1
  .. ..$ m2 : num 0.819
  .. ..$ m3 : num 2.1
  .. ..$ m4 : num 0.578
  .. ..$ m5 : num 1.98
  .. ..$ m6 : num 0.186
  .. ..$ m7 : num 0.361
  .. ..$ m8 : num 0.834
  .. ..$ m9 : num 0.397
  .. ..$ m10: num 0.93
  .. ..$ m11: num 0.887
  .. ..$ q  : num 0.907
  .. ..$ qm2: num 0.918
  ..$ diagnostics  :List of 7
  .. ..$ vardecomposition:List of 6
  .. .. ..$ cycle    : num 0.196
  .. .. ..$ seasonal : num 0.279
  .. .. ..$ irregular: num 0.0373
  .. .. ..$ calendar : num 0.0256
  .. .. ..$ others   : num 0.545
  .. .. ..$ total    : num 1.08
  .. ..$ seas.ftest.i    :List of 2
  .. .. ..$ value : num 0.546
  .. .. ..$ pvalue: num 0.872
  .. .. ..- attr(*, "distribution")= chr "F with 11.0 degrees of freedom in the nominator and 395.0 degrees of freedom in the denominator"
  .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. ..$ seas.ftest.sa   :List of 2
  .. .. ..$ value : num 0.133
  .. .. ..$ pvalue: num 1
  .. .. ..- attr(*, "distribution")= chr "F with 11.0 degrees of freedom in the nominator and 393.0 degrees of freedom in the denominator"
  .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. ..$ seas.qstest.i   :List of 2
  .. .. ..$ value : num 0
  .. .. ..$ pvalue: num 1
  .. .. ..- attr(*, "distribution")= chr "Chi2 with 2.0 degrees of freedom "
  .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. ..$ seas.qstest.sa  :List of 2
  .. .. ..$ value : num 0
  .. .. ..$ pvalue: num 1
  .. .. ..- attr(*, "distribution")= chr "Chi2 with 2.0 degrees of freedom "
  .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. ..$ td.ftest.i      :List of 2
  .. .. ..$ value : num 2.39
  .. .. ..$ pvalue: num 0.0279
  .. .. ..- attr(*, "distribution")= chr "F with 6.0 degrees of freedom in the nominator and 401.0 degrees of freedom in the denominator"
  .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  .. ..$ td.ftest.sa     :List of 2
  .. .. ..$ value : num 2.29
  .. .. ..$ pvalue: num 0.0345
  .. .. ..- attr(*, "distribution")= chr "F with 6.0 degrees of freedom in the nominator and 401.0 degrees of freedom in the denominator"
  .. .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..- attr(*, "class")= chr "JD3_X13_RSLTS"
 $ estimation_spec:List of 3
  ..$ regarima    :List of 7
  .. ..$ basic     :List of 3
  .. .. ..$ span            :List of 5
  .. .. .. ..$ type: chr "ALL"
  .. .. .. ..$ d0  : NULL
  .. .. .. ..$ d1  : NULL
  .. .. .. ..$ n0  : int 0
  .. .. .. ..$ n1  : int 0
  .. .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. .. ..$ preprocessing   : logi TRUE
  .. .. ..$ preliminaryCheck: logi TRUE
  .. ..$ transform :List of 4
  .. .. ..$ fn      : chr "LOG"
  .. .. ..$ adjust  : chr "LEAPYEAR"
  .. .. ..$ aicdiff : num -2
  .. .. ..$ outliers: logi TRUE
  .. ..$ outlier   :List of 7
  .. .. ..$ outliers     :List of 3
  .. .. .. ..$ :List of 2
  .. .. .. .. ..$ type: chr "AO"
  .. .. .. .. ..$ va  : num 0
  .. .. .. ..$ :List of 2
  .. .. .. .. ..$ type: chr "LS"
  .. .. .. .. ..$ va  : num 0
  .. .. .. ..$ :List of 2
  .. .. .. .. ..$ type: chr "TC"
  .. .. .. .. ..$ va  : num 0
  .. .. ..$ span         :List of 5
  .. .. .. ..$ type: chr "ALL"
  .. .. .. ..$ d0  : NULL
  .. .. .. ..$ d1  : NULL
  .. .. .. ..$ n0  : int 0
  .. .. .. ..$ n1  : int 0
  .. .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. .. ..$ defva        : num 0
  .. .. ..$ method       : chr "ADDONE"
  .. .. ..$ monthlytcrate: num 0.7
  .. .. ..$ maxiter      : int 30
  .. .. ..$ lsrun        : int 0
  .. ..$ arima     :List of 7
  .. .. ..$ period: int 0
  .. .. ..$ d     : int 1
  .. .. ..$ bd    : int 1
  .. .. ..$ phi   : NULL
  .. .. ..$ theta :List of 2
  .. .. .. ..$ : num 0
  .. .. .. ..$ : chr "UNDEFINED"
  .. .. .. ..- attr(*, "dim")= int [1:2] 2 1
  .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. ..$ : NULL
  .. .. ..$ bphi  : NULL
  .. .. ..$ btheta:List of 2
  .. .. .. ..$ : num 0
  .. .. .. ..$ : chr "UNDEFINED"
  .. .. .. ..- attr(*, "dim")= int [1:2] 2 1
  .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. ..$ : NULL
  .. .. ..- attr(*, "class")= chr "JD3_SARIMA_ESTIMATION"
  .. ..$ automodel :List of 12
  .. .. ..$ enabled  : logi TRUE
  .. .. ..$ ljungbox : num 0.95
  .. .. ..$ tsig     : num 1
  .. .. ..$ predcv   : num 0.143
  .. .. ..$ ubfinal  : num 1.05
  .. .. ..$ ub1      : num 1.03
  .. .. ..$ ub2      : num 1.14
  .. .. ..$ cancel   : num 0.1
  .. .. ..$ fct      : num 1.01
  .. .. ..$ acceptdef: logi FALSE
  .. .. ..$ mixed    : logi TRUE
  .. .. ..$ balanced : logi FALSE
  .. ..$ regression:List of 8
  .. .. ..$ mean         : NULL
  .. .. ..$ check_mean   : logi FALSE
  .. .. ..$ td           :List of 12
  .. .. .. ..$ td            : chr "TD_NONE"
  .. .. .. ..$ lp            : chr "NONE"
  .. .. .. ..$ holidays      : chr ""
  .. .. .. ..$ users         : chr [1:6] "r.Monday" "r.Tuesday" "r.Wednesday" "r.Thursday" ...
  .. .. .. ..$ w             : int 0
  .. .. .. ..$ test          : chr "NO"
  .. .. .. ..$ auto          : chr "AUTO_NO"
  .. .. .. ..$ autoadjust    : logi FALSE
  .. .. .. ..$ tdcoefficients:List of 12
  .. .. .. .. ..$ : num 0
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..- attr(*, "dim")= int [1:2] 2 6
  .. .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. .. ..$ : NULL
  .. .. .. ..$ lpcoefficient : NULL
  .. .. .. ..$ ptest1        : num 0
  .. .. .. ..$ ptest2        : num 0
  .. .. ..$ easter       :List of 4
  .. .. .. ..$ type       : chr "JULIAN"
  .. .. .. ..$ duration   : int 8
  .. .. .. ..$ test       : chr "NO"
  .. .. .. ..$ coefficient: NULL
  .. .. ..$ outliers     : NULL
  .. .. ..$ users        :List of 1
  .. .. .. ..$ :List of 5
  .. .. .. .. ..$ id       : chr "r.reg1"
  .. .. .. .. ..$ name     : chr "iv1"
  .. .. .. .. ..$ lag      : int 0
  .. .. .. .. ..$ coef     :List of 2
  .. .. .. .. .. ..$ value: num 0
  .. .. .. .. .. ..$ type : chr "UNDEFINED"
  .. .. .. .. ..$ regeffect: chr "Trend"
  .. .. ..$ interventions: NULL
  .. .. ..$ ramps        : NULL
  .. ..$ estimate  :List of 2
  .. .. ..$ span:List of 5
  .. .. .. ..$ type: chr "FROM"
  .. .. .. ..$ d0  : Date[1:1], format: "2012-01-01"
  .. .. .. ..$ d1  : NULL
  .. .. .. ..$ n0  : int 0
  .. .. .. ..$ n1  : int 0
  .. .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. .. ..$ tol : num 1e-07
  .. ..- attr(*, "class")= chr "JD3_REGARIMA_SPEC"
  ..$ x11         :List of 12
  .. ..$ mode         : chr "UNKNOWN"
  .. ..$ seasonal     : logi TRUE
  .. ..$ henderson    : int 0
  .. ..$ sfilters     : chr "FILTER_MSR"
  .. ..$ lsig         : num 1.5
  .. ..$ usig         : num 2.5
  .. ..$ nfcasts      : int -1
  .. ..$ nbcasts      : int 0
  .. ..$ sigma        : chr "NONE"
  .. ..$ vsigmas      : int(0) 
  .. ..$ excludefcasts: logi FALSE
  .. ..$ bias         : chr "RATIO"
  .. ..- attr(*, "class")= chr "JD3_X11_SPEC"
  ..$ benchmarking:List of 6
  .. ..$ enabled : logi TRUE
  .. ..$ target  : chr "TARGET_ORIGINAL"
  .. ..$ lambda  : num 0.5
  .. ..$ rho     : num 0.8
  .. ..$ bias    : chr "BIAS_NONE"
  .. ..$ forecast: logi FALSE
  ..- attr(*, "class")= chr "JD3_X13_SPEC"
 $ result_spec    :List of 3
  ..$ regarima    :List of 7
  .. ..$ basic     :List of 3
  .. .. ..$ span            :List of 5
  .. .. .. ..$ type: chr "ALL"
  .. .. .. ..$ d0  : NULL
  .. .. .. ..$ d1  : NULL
  .. .. .. ..$ n0  : int 0
  .. .. .. ..$ n1  : int 0
  .. .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. .. ..$ preprocessing   : logi TRUE
  .. .. ..$ preliminaryCheck: logi TRUE
  .. ..$ transform :List of 4
  .. .. ..$ fn      : chr "LOG"
  .. .. ..$ adjust  : chr "LEAPYEAR"
  .. .. ..$ aicdiff : num -2
  .. .. ..$ outliers: logi TRUE
  .. ..$ outlier   :List of 7
  .. .. ..$ outliers     : list()
  .. .. ..$ span         :List of 5
  .. .. .. ..$ type: chr "ALL"
  .. .. .. ..$ d0  : NULL
  .. .. .. ..$ d1  : NULL
  .. .. .. ..$ n0  : int 0
  .. .. .. ..$ n1  : int 0
  .. .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. .. ..$ defva        : num 0
  .. .. ..$ method       : chr "ADDONE"
  .. .. ..$ monthlytcrate: num 0.7
  .. .. ..$ maxiter      : int 30
  .. .. ..$ lsrun        : int 0
  .. ..$ arima     :List of 7
  .. .. ..$ period: int 12
  .. .. ..$ d     : int 1
  .. .. ..$ bd    : int 1
  .. .. ..$ phi   : NULL
  .. .. ..$ theta :List of 2
  .. .. .. ..$ : num -0.771
  .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. ..- attr(*, "dim")= int [1:2] 2 1
  .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. ..$ : NULL
  .. .. ..$ bphi  : NULL
  .. .. ..$ btheta:List of 2
  .. .. .. ..$ : num -0.726
  .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. ..- attr(*, "dim")= int [1:2] 2 1
  .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. ..$ : NULL
  .. .. ..- attr(*, "class")= chr "JD3_SARIMA_ESTIMATION"
  .. ..$ automodel :List of 12
  .. .. ..$ enabled  : logi FALSE
  .. .. ..$ ljungbox : num 0.95
  .. .. ..$ tsig     : num 1
  .. .. ..$ predcv   : num 0.143
  .. .. ..$ ubfinal  : num 1.05
  .. .. ..$ ub1      : num 1.03
  .. .. ..$ ub2      : num 1.14
  .. .. ..$ cancel   : num 0.1
  .. .. ..$ fct      : num 1.01
  .. .. ..$ acceptdef: logi FALSE
  .. .. ..$ mixed    : logi TRUE
  .. .. ..$ balanced : logi FALSE
  .. ..$ regression:List of 8
  .. .. ..$ mean         : NULL
  .. .. ..$ check_mean   : logi FALSE
  .. .. ..$ td           :List of 12
  .. .. .. ..$ td            : chr "TD_NONE"
  .. .. .. ..$ lp            : chr "NONE"
  .. .. .. ..$ holidays      : chr ""
  .. .. .. ..$ users         : chr [1:6] "r.Monday" "r.Tuesday" "r.Wednesday" "r.Thursday" ...
  .. .. .. ..$ w             : int 0
  .. .. .. ..$ test          : chr "NO"
  .. .. .. ..$ auto          : chr "AUTO_NO"
  .. .. .. ..$ autoadjust    : logi FALSE
  .. .. .. ..$ tdcoefficients:List of 12
  .. .. .. .. ..$ : num -0.00786
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0.0183
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0.00349
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0.0156
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num 0.022
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..$ : num -0.0207
  .. .. .. .. ..$ : chr "ESTIMATED"
  .. .. .. .. ..- attr(*, "dim")= int [1:2] 2 6
  .. .. .. .. ..- attr(*, "dimnames")=List of 2
  .. .. .. .. .. ..$ : chr [1:2] "value" "type"
  .. .. .. .. .. ..$ : NULL
  .. .. .. ..$ lpcoefficient : NULL
  .. .. .. ..$ ptest1        : num 0
  .. .. .. ..$ ptest2        : num 0
  .. .. ..$ easter       :List of 4
  .. .. .. ..$ type       : chr "STANDARD"
  .. .. .. ..$ duration   : int 8
  .. .. .. ..$ test       : chr "NO"
  .. .. .. ..$ coefficient:List of 2
  .. .. .. .. ..$ value: num -0.0633
  .. .. .. .. ..$ type : chr "ESTIMATED"
  .. .. ..$ outliers     :List of 2
  .. .. .. ..$ :List of 4
  .. .. .. .. ..$ name: chr "TC (2020-03-01)"
  .. .. .. .. ..$ pos : Date[1:1], format: "2020-03-01"
  .. .. .. .. ..$ code: chr "TC"
  .. .. .. .. ..$ coef:List of 2
  .. .. .. .. .. ..$ value: num -0.257
  .. .. .. .. .. ..$ type : chr "ESTIMATED"
  .. .. .. ..$ :List of 4
  .. .. .. .. ..$ name: chr "LS (2020-04-01)"
  .. .. .. .. ..$ pos : Date[1:1], format: "2020-04-01"
  .. .. .. .. ..$ code: chr "LS"
  .. .. .. .. ..$ coef:List of 2
  .. .. .. .. .. ..$ value: num -0.448
  .. .. .. .. .. ..$ type : chr "ESTIMATED"
  .. .. ..$ users        :List of 1
  .. .. .. ..$ :List of 5
  .. .. .. .. ..$ id       : chr "r.reg1"
  .. .. .. .. ..$ name     : chr "iv1"
  .. .. .. .. ..$ lag      : int 0
  .. .. .. .. ..$ coef     :List of 2
  .. .. .. .. .. ..$ value: num -0.0436
  .. .. .. .. .. ..$ type : chr "ESTIMATED"
  .. .. .. .. ..$ regeffect: chr "Trend"
  .. .. ..$ interventions: NULL
  .. .. ..$ ramps        : NULL
  .. ..$ estimate  :List of 2
  .. .. ..$ span:List of 5
  .. .. .. ..$ type: chr "FROM"
  .. .. .. ..$ d0  : Date[1:1], format: "2012-01-01"
  .. .. .. ..$ d1  : NULL
  .. .. .. ..$ n0  : int 0
  .. .. .. ..$ n1  : int 0
  .. .. .. ..- attr(*, "class")= chr "JD3_SPAN"
  .. .. ..$ tol : num 1e-07
  .. ..- attr(*, "class")= chr "JD3_REGARIMA_SPEC"
  ..$ x11         :List of 12
  .. ..$ mode         : chr "UNKNOWN"
  .. ..$ seasonal     : logi TRUE
  .. ..$ henderson    : int 0
  .. ..$ sfilters     : chr "FILTER_MSR"
  .. ..$ lsig         : num 1.5
  .. ..$ usig         : num 2.5
  .. ..$ nfcasts      : int -1
  .. ..$ nbcasts      : int 0
  .. ..$ sigma        : chr "NONE"
  .. ..$ vsigmas      : int(0) 
  .. ..$ excludefcasts: logi FALSE
  .. ..$ bias         : chr "RATIO"
  .. ..- attr(*, "class")= chr "JD3_X11_SPEC"
  ..$ benchmarking:List of 6
  .. ..$ enabled : logi TRUE
  .. ..$ target  : chr "TARGET_ORIGINAL"
  .. ..$ lambda  : num 0.5
  .. ..$ rho     : num 0.8
  .. ..$ bias    : chr "BIAS_NONE"
  .. ..$ forecast: logi FALSE
  ..- attr(*, "class")= chr "JD3_X13_SPEC"
 $ user_defined   :List of 334
  ..$ period                              : num 12
  ..$ span.start                          : chr "1990-01-01T00:00:00/P1M"
  ..$ span.end                            : chr "2024-01-01T00:00:00/P1M"
  ..$ span.n                              : num 409
  ..$ span.missing                        : num 0
  ..$ log                                 : num 1
  ..$ adjust                              : chr "LeapYear"
  ..$ likelihood.ll                       : num 158
  ..$ likelihood.adjustedll               : num -487
  ..$ likelihood.ssqerr                   : num 0.658
  ..$ likelihood.aic                      : num 1000
  ..$ likelihood.bic                      : num 1038
  ..$ likelihood.aicc                     : num 1003
  ..$ likelihood.bicc                     : num -4.86
  ..$ likelihood.bic2                     : num -1.91
  ..$ likelihood.hannanquinn              : num 1015
  ..$ likelihood.nparams                  : num 13
  ..$ likelihood.nobs                     : num 145
  ..$ likelihood.neffectiveobs            : num 132
  ..$ likelihood.df                       : num 119
  ..$ arima.p                             : num 0
  ..$ arima.d                             : num 1
  ..$ arima.q                             : num 1
  ..$ arima.bp                            : num 0
  ..$ arima.bd                            : num 1
  ..$ arima.bq                            : num 1
  ..$ arima.theta(*)                      : num [1, 1:4] -0.771 0.0507 -15.2156 0
  .. ..- attr(*, "dimnames")=List of 2
  .. .. ..$ : NULL
  .. .. ..$ : chr [1:4] "Estimate" "Std. Error" "T-stat" "Pr(>|t|)"
  ..$ arima.phi(*)                        : NULL
  ..$ arima.btheta(*)                     : num [1, 1:4] -7.26e-01 1.05e-01 -6.89 2.86e-10
  .. ..- attr(*, "dimnames")=List of 2
  .. .. ..$ : NULL
  .. .. ..$ : chr [1:4] "Estimate" "Std. Error" "T-stat" "Pr(>|t|)"
  ..$ arima.bphi(*)                       : NULL
  ..$ regression.espan.start              : chr "2012-01-01T00:00:00/P1M"
  ..$ regression.espan.end                : chr "2024-01-01T00:00:00/P1M"
  ..$ regression.espan.n                  : num 145
  ..$ regression.espan.missing            : num 0
  ..$ regression.mean                     : num 0
  ..$ regression.nlp                      : num 0
  ..$ regression.ntd                      : num 6
  ..$ regression.leaster                  : num 0
  ..$ regression.nmh                      : num 1
  ..$ regression.nout                     : num 2
  ..$ regression.nao                      : num 0
  ..$ regression.nls                      : num 1
  ..$ regression.ntc                      : num 1
  ..$ regression.nso                      : num 0
  ..$ regression.nusers                   : num 1
  ..$ regression.mu                       : NULL
  ..$ regression.lp                       : NULL
  ..$ regression.td(*)                    : num [1, 1:4] -0.00786 0.00896 -0.87736 0.38204
  .. ..- attr(*, "dimnames")=List of 2
  .. .. ..$ : chr "r.Monday"
  .. .. ..$ : chr [1:4] "Estimate" "Std. Error" "T-stat" "Pr(>|t|)"
  ..$ regression.td-derived               : NULL
  ..$ regression.td-ftest                 :List of 2
  .. ..$ value : num 7.4
  .. ..$ pvalue: num 9.5e-07
  .. ..- attr(*, "distribution")= chr "F with 6.0 degrees of freedom in the nominator and 120.0 degrees of freedom in the denominator"
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ regression.easter                   : num [1, 1:4] -0.0633 0.0882 -0.718 0.4741
  .. ..- attr(*, "dimnames")=List of 2
  .. .. ..$ : chr "julian easter [8]"
  .. .. ..$ : chr [1:4] "Estimate" "Std. Error" "T-stat" "Pr(>|t|)"
  ..$ regression.outlier(*)               : num [1, 1:4] -2.57e-01 5.86e-02 -4.40 2.39e-05
  .. ..- attr(*, "dimnames")=List of 2
  .. .. ..$ : chr "TC (2020-03)"
  .. .. ..$ : chr [1:4] "Estimate" "Std. Error" "T-stat" "Pr(>|t|)"
  ..$ regression.user(*)                  : num [1, 1:4] -0.0436 0.0301 -1.4481 0.1502
  .. ..- attr(*, "dimnames")=List of 2
  .. .. ..$ : chr "iv1"
  .. .. ..$ : chr [1:4] "Estimate" "Std. Error" "T-stat" "Pr(>|t|)"
  ..$ regression.missing(*)               : NULL
  ..$ residuals.res                       : num [1:122] -0.1483 -0.0517 -0.0366 -0.0213 -0.04 ...
  ..$ residuals.tsres                     : Time-Series [1:132] from 2013 to 2024: 0.1298 -0.0698 0.0427 0.0719 0.1076 ...
  ..$ residuals.n                         : num 132
  ..$ residuals.df                        : num 122
  ..$ residuals.dfc                       : num 120
  ..$ residuals.ser                       : num 0.0741
  ..$ residuals.ser_ml                    : num 0.0706
  ..$ residuals.type                      : chr "QR_Transformed"
  ..$ residuals.mean                      :List of 2
  .. ..$ value : num -0.31
  .. ..$ pvalue: num 0.757
  .. ..- attr(*, "distribution")= chr "T with 132.0 degrees of freedom"
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.skewness                  :List of 2
  .. ..$ value : num 0.183
  .. ..$ pvalue: num 0.392
  .. ..- attr(*, "distribution")= chr "Normal with Mean = 0.0 and Stdev = 0.21320071635561044"
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.kurtosis                  :List of 2
  .. ..$ value : num 2.97
  .. ..$ pvalue: num 0.938
  .. ..- attr(*, "distribution")= chr "Normal with Mean = 3.0 and Stdev = 0.4264014327112209"
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.doornikhansen             :List of 2
  .. ..$ value : num 0.825
  .. ..$ pvalue: num 0.662
  .. ..- attr(*, "distribution")= chr "Chi2 with 2.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.lb                        :List of 2
  .. ..$ value : num 24.2
  .. ..$ pvalue: num 0.337
  .. ..- attr(*, "distribution")= chr "Chi2 with 22.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.bp                        :List of 2
  .. ..$ value : num 22
  .. ..$ pvalue: num 0.461
  .. ..- attr(*, "distribution")= chr "Chi2 with 22.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.lb2                       :List of 2
  .. ..$ value : num 36.4
  .. ..$ pvalue: num 0.0275
  .. ..- attr(*, "distribution")= chr "Chi2 with 22.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.bp2                       :List of 2
  .. ..$ value : num 32.2
  .. ..$ pvalue: num 0.0747
  .. ..- attr(*, "distribution")= chr "Chi2 with 22.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.seaslb                    :List of 2
  .. ..$ value : num 0.295
  .. ..$ pvalue: num 0.863
  .. ..- attr(*, "distribution")= chr "Chi2 with 2.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.seasbp                    :List of 2
  .. ..$ value : num 0.26
  .. ..$ pvalue: num 0.878
  .. ..- attr(*, "distribution")= chr "Chi2 with 2.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.nruns                     :List of 2
  .. ..$ value : num 1.01
  .. ..$ pvalue: num 0.31
  .. ..- attr(*, "distribution")= chr "Normal with Mean = 0.0 and Stdev = 1.0"
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.lruns                     :List of 2
  .. ..$ value : num 14.8
  .. ..$ pvalue: num 1
  .. ..- attr(*, "distribution")= chr "Chi2 with 132.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.nudruns                   :List of 2
  .. ..$ value : num 0.277
  .. ..$ pvalue: num 0.782
  .. ..- attr(*, "distribution")= chr "Normal with Mean = 0.0 and Stdev = 1.0"
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ residuals.ludruns                   :List of 2
  .. ..$ value : num 1.66
  .. ..$ pvalue: num 1
  .. ..- attr(*, "distribution")= chr "Chi2 with 131.0 degrees of freedom "
  .. ..- attr(*, "class")= chr [1:2] "JD3_TEST" "JD3"
  ..$ regression.ml.parameters            : num [1:2] -0.771 -0.726
  ..$ regression.ml.pcovar                : num [1:2, 1:2] 2.61e-03 -6.36e-05 -6.36e-05 1.13e-02
  ..$ regression.ml.pcovar-ml             : num [1:2, 1:2] 2.35e-03 -5.74e-05 -5.74e-05 1.02e-02
  ..$ regression.ml.pcorr                 : num [1:2, 1:2] 1 -0.0117 -0.0117 1
  ..$ regression.ml.pscore                : num [1:2] 0.02026 -0.00422
  ..$ regression.details.description      : chr [1:10] "iv1" "r.Monday" "r.Tuesday" "r.Wednesday" ...
  ..$ regression.details.type             : int [1:10] 2 6 6 6 6 6 6 6 5 2
  ..$ regression.details.coefficients     : num [1:10] -0.04359 -0.00786 0.01831 0.00349 0.01563 ...
  ..$ regression.details.covar            : num [1:10, 1:10] 9.06e-04 1.80e-07 -1.21e-05 3.23e-05 -4.52e-05 ...
  ..$ regression.details.covar-ml         : num [1:10, 1:10] 8.17e-04 1.62e-07 -1.09e-05 2.91e-05 -4.08e-05 ...
  ..$ y                                   : Time-Series [1:409] from 1990 to 2024: 107.3 96.4 102.6 78.5 71.7 ...
  ..$ y_f(?)                              : Time-Series [1:12] from 2024 to 2025: 121 135 128 112 142 ...
  ..$ y_ef(?)                             : Time-Series [1:12] from 2024 to 2025: 8.82 10.4 11.35 10.2 11.7 ...
  ..$ y_b(?)                              : NULL
  ..$ y_eb(?)                             : NULL
  ..$ yc                                  : Time-Series [1:409] from 1990 to 2024: 107.3 96.4 102.6 78.5 71.7 ...
  ..$ yc_f(?)                             : Time-Series [1:12] from 2024 to 2025: 121 135 128 112 142 ...
  ..$ yc_b(?)                             : NULL
  ..$ ylin                                : Time-Series [1:409] from 1990 to 2024: 67.1 62.1 64 52.7 45 ...
  ..$ ylin_f(?)                           : Time-Series [1:12] from 2024 to 2025: 118 135 125 115 142 ...
  ..$ ylin_b(?)                           : NULL
  ..$ det                                 : Time-Series [1:409] from 1990 to 2024: 1.6 1.55 1.6 1.49 1.59 ...
  ..$ det_f(?)                            : Time-Series [1:12] from 2024 to 2025: 1.027 1.002 1.025 0.974 1 ...
  .. [list output truncated]
  ..- attr(*, "class")= chr "user_defined"
 - attr(*, "class")= chr "JD3_X13_OUTPUT"
> 



sa_x13_ud$user_defined$period



